Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-05-04 paper/tidy-missing-data-paper.Rmd
tidying up some wording in the nabular data section

_Nabular_ data binds the shadow matrix column-wise to the original data. It is a portmanteau of `NA` and `tabular`. _Nabular_ data keeps corresponding rows together, removing the possibility of mismatching records, explicitly linking missing values to data. _Nabular_ data facilitates visualization and summaries by allowing the user to reference the missingness of a variable, `var`, as `var_NA`. _Nabular_ data is a snapshot of the missingness of the data. This means when _nabular_ data is imputed, those imputed values can easily be identified in analysis by referring to the coordinated names. _Nabular_ data is created with `nabular(data)` (Figure \@ref(fig:nabularfig)). _Nabular_ data is not unlike classical data formats with quality or flag columns associated with each measured variable, e.g. Scripps CO2 data [@Keeling2005-scripps], GHCN data [@Durre2008-ghcn].

@@

The _nabular_ data structure provides three key benefits over on-the-fly creating a missingness matrix $B$. Firstly, missing value labels `NA` and `!NA` are clearer than TRUE or FALSE. Secondly, special missing values cannot be added easily during analysis with a logical matrix. Finally, the logical matrix cannot capture which values are imputed, if imputation has already taken place. Imputing values on _nabular_ data automatically tracks these value changes.

>>>>

_Nabular_ data binds the shadow matrix column-wise to the original data. It is a portmanteau of `NA` and `tabular`. _Nabular_ explicitly links missing values to data, keeping corresponding observations together and removing the possibility of mismatching records. _Nabular_ data facilitates visualization and summaries by allowing the user to reference the missingness of a variable, `var`, as `var_NA`. _Nabular_ data is a snapshot of the missingness of the data. This means when _nabular_ data is imputed, those imputed values can easily be identified in analysis by referring to the coordinated names.  _Nabular_ data is not unlike classical data formats with quality or flag columns associated with each measured variable, e.g. Scripps CO2 data [@Keeling2005-scripps], GHCN data [@Durre2008-ghcn]. _Nabular_ data is created with `nabular(data)` (Figure \@ref(fig:nabularfig)).

@@

The _nabular_ data structure provides three key benefits over creating a missingness matrix, $B$, on-the-fly. Firstly, missing value labels `NA` and `!NA` are clearer than TRUE or FALSE. Secondly, special missing values cannot be added easily during analysis with a logical matrix. Finally, the logical matrix cannot capture which values are imputed, if imputation has already taken place. Imputing values on _nabular_ data automatically tracks these imputations.
